---
title: "bettr"
author: "Charlotte Soneson & Federico Marini"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bettr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

`bettr` is an R package that allows the user to launch an interactive interface 
for exploring rankings. For example, it could be used to explore the ranking of 
methods in a benchmarking effort, where multiple criteria have been evaluated.
The user can weight the different criteria according to their preferences, and 
visualize the data in several different ways. 

# Installation

`bettr` can be installed from GitHub: 

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("federicomarini/bettr")
```

# Usage

The input to `bettr` is a `data.frame` containing values of several metrics 
for several methods. In addition, the user can provide additional annotations 
and characteristics for the methods and metrics, which can be used to group and 
filter them in the interactive application. 

```{r}
## Data for two metrics (metric1, metric2) for three methods (M1, M2, M3)
df <- data.frame(Method = c("M1", "M2", "M3"), 
                 metric1 = c(1, 2, 3),
                 metric2 = c(3, 1, 2))

## More information for metrics
metricInfo <- data.frame(Metric = c("metric1", "metric2", "metric3"),
                         Group = c("G1", "G2", "G2"))

## More information for methods ('IDs')
idInfo <- data.frame(Method = c("M1", "M2", "M3"), 
                     Type = c("T1", "T1", "T2"))
```

```{r, eval=interactive()}
## Launch app
bettr(df = df, idCol = "Method", metricInfo = metricInfo, idInfo = idInfo)
```

# Session info

```{r}
sessionInfo()
```

